\documentclass[11pt]{article}
\usepackage{listings}
\usepackage{hyperref}

\lstset {
basicstyle={\ttfamily, \footnotesize},
showspaces=false, showstringspaces=false
}
\begin{document}

\title{Csound for Portable Native Client}
\author{Victor Lazzarini}
\date{\today}
\maketitle

\section{Introduction}

Native Client (NaCl) is a sandboxing technology developed by Google that allows C/C++ modules to extend the support provided
by HTML5. Portable Native Client (pNaCl) is one of the toolchains in the NaCl SDK (the others are newlib and glibc). The advantage
of pNaCl over the other options is that it only requires a single module to be built for all supported architectures.

The other major advantage is that pNaCl is, as of Google Chrome 31, enabled by default in the browser. This means that users
just need to load a page containing the pNaCl application and it will work. pNaCl modules are compiled to llvm bytecode that is 
translated to a native binary by the browser. To check whether your version of Chrome supports pNaCl, use the following address:
\\

 {\tt chrome://nacl }
\\

The pNaCl Csound implementation allows users to embed the system in web pages. With a minimal use of Javascript, it is possible
to create applications and frontends for Csound, to be run inside a web browser (Chrome, Chromium).

A binary package for pNaCl-Csound can be found in the Csound releases \url{http://sourceforge.net/projects/csound/files/csound6}

\subsection{Running the example application}

NaCl pages need to be served over http, which means they will not work
when opened as local files. For this you will need a http server. A
minimal one, written in Python, can be found in the NaCl SDK 
\url{https://developer.chrome.com/native-client/sdk/download}.

\section{Csound pNaCl module reference}

The interface to Csound is found in the csound.js javascript file. Csound is ready on module load, and can accept control messages
from then on.

\subsection{Control functions}

The following control functions can be used to interact with Csound:

\begin{itemize}
\item {\tt csound.Play()} - starts performance
\item {\tt csound.PlayCsd(s)} - starts performance from a CSD file s, which can be in ./http/ (ORIGIN server) or ./local/ (local sandbox).
\item {\tt csound.RenderCsd(s)} - renders a CSD file s, which can be in ./http/ (ORIGIN server) or ./local/ (local sandbox), with no RT audio output.
The ``finished render" message is issued on completion.
\item {\tt csound.Pause()} - pauses performance
\item  {\tt csound.StartAudioInput()} - switches on audio input
  (available in Chrome version 36 onwards)
\item {\tt csound.CompileOrc(s)} - compiles the Csound code in the string s
\item {\tt csound.ReadScore(s)} - reads the score in the string s (with preprocessing support)
\item {\tt csound.Event(s)} - sends in the line events contained in the string s (no preprocessing)
\item {\tt csound.SetChannel(name, value)} - sends the control channel
  \emph{name} the value \emph{value}.
\item {\tt csound.SetStringChannel(name, string)} - sends the string channel
  \emph{name} the string \emph{string}.
\item {\tt csound.SetTable(num, pos, value)} - sets the table
  \emph{name} at index \emph{pos} the value \emph{value}.
\item {\tt csound.RequestTable(num)} - requests the table data for
  table \emph{num}. The ``Table::Complete" message is issued on completion. 
\item {\tt csound.GetTableData()} - returns the most recently
  requested table data as an ArrayObject. 
\item {\tt MIDIin(byte1, byte2, byte3)} - sends a MIDI in message to Csound.
\item {\tt NoteOn(channel,number,velocity)} - sends a Note ON message to Csound.
\item {\tt NoteOff(channel,number,velocity)} - sends a Note OFF message to Csound.
\item {\tt PolyAftertouch(channel,number,aftertouch)} - sends a polyphonic aftertouch message to Csound.
\item {\tt ControlChange(channel,control,amount)} - sends a control change message to Csound.
\item {\tt ProgramChange(channel,control)} - sends a program change message to Csound.
\item {\tt Aftertouch(channel,amount)} - sends a mono aftertouch message to Csound.
\item {\tt PitchBend(channel,fine,coarse)} - sends a pitchbend message to Csound.
\end{itemize}

\subsection{Filesystem functions}

In order to facilitate access to files, the following filesystem functions can be used:

\begin{itemize}
\item {\tt csound.CopyToLocal(src, dest)} - copies the file \emph{src} in the ORIGIN directory to the local file \emph{dest}, which can
be accessed at ./local/\emph{dest}. The ``Complete" message is issued on completion.
\item {\tt csound.CopyUrlToLocal(url,dest)} - copies the url \emph{url} to the local file \emph{dest}, which can
be accessed at ./local/\emph{dest}. Currently only ORIGIN and CORS urls are allowed remotely, but local files can
also be passed if encoded as urls with the webkitURL.createObjectURL() javascript method. The ``Complete" message is issued on completion.
\item {\tt csound.RequestFileFromLocal(src)} - requests the data from the local file \emph{src}. The ``Complete" message is issued on completion. 
\item {\tt csound.GetFileData()} - returns the most recently requested file data as an ArrayObject.
\end{itemize}


\subsection{Callbacks}

The csound.js module will call the following window functions when it starts:

\begin{itemize} 
\item {\tt function moduleDidLoad()}: this is called as soon as the module is loaded 
\item {\tt function handleMessage(message)}: called when there are messages from Csound (pnacl module). 
The string message.data contains the message.
\item {\tt function attachListeners()}: this is called when listeners for different events are to be attached. 
\end{itemize}

You should implement these functions in your HTML page script, in order to use the Csound javascript interface.
In addition to the above, Csound javascript module messages are always sent to the HTML element with id=`console', 
which is normally of type \textless div\textgreater \, or \textless textarea\textgreater .

\subsection{Example}

Here is a minimal HTML example showing the use of Csound

\lstinputlisting[language=HTML]{../minimal.html}

\section{Limitations}

The following limitations apply:

\begin{itemize}
\item MIDI is implemented so that Csound MIDI opcodes can be used. MIDI hardware interface needs to be provided
in Javascript by another library (e.g. WebMIDI).
\item no plugins, as pNaCl does not support dlopen() and friends. This means some opcodes are not available as they reside in plugin libraries.
It might be possible to add some of these opcodes statically to the Csound pNaCl library in the future.
\end {itemize}

\end{document}
