\begin{comment}
\documentclass[10pt]{article}
\usepackage{fullpage, graphicx, url}
\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\title{distort1}
\begin{document}


\begin{tabular}{ccc}
The Alternative Csound Reference Manual & & \\
Previous & &Next

\end{tabular}

%\hline 
\end{comment}
\section{distort1}
distort1 --  Modified hyperbolic tangent distortion. \subsection*{Description}


  Implementation of modified hyperbolic tangent distortion. \emph{distort1}
 can be used to generate wave shaping distortion based on a modification of the \emph{tanh}
 function. 


 


          exp(asig * (pregain + shape1)) - exp(asig*(pregain+shape2))\\ 
   aout = -----------------------------------------------------------\\ 
          exp(asig*pregain)              + exp(-asig*pregain)\\ 
       
\subsection*{Syntax}


 ar \textbf{distort1}
 asig, kpregain, kpostgain, kshape1, kshape2
\subsection*{Performance}


 \emph{asig - }
is the input signal. 


 \emph{kpregain}
 -- determines the amount of gain applied to the signal before waveshaping. A value of 1 gives slight distortion. 


 \emph{kpostgain}
 -- determines the amount of gain applied to the signal after waveshaping. 


 \emph{kshape1}
 -- determines the shape of the positive part of the curve. A value of 0 gives a flat clip, small positive values give sloped shaping. 


 \emph{kshape2}
 -- determines the shape of the negative part of the curve. 
\subsection*{Examples}


  Here is an example of the distort1 opcode. It uses the files \emph{distort1.orc}
 and \emph{distort1.sco}
. 


 \textbf{Example 1. Example of the distort1 opcode.}

\begin{lstlisting}
/* distort1.orc */
; Initialize the global variables.
sr = 44100
kr = 4410
ksmps = 10
nchnls = 2

gadist init 0
  
instr 1
  iamp = p4
  ifqc = cpspch(p5)
  asig pluck iamp, ifqc, ifqc, 0, 1
  gadist = gadist + asig
endin
  
instr 50
  kpre init p4
  kpost init p5
  kshap1 init p6
  kshap2 init p7
  aout distort1 gadist, kpre, kpost, kshap1, kshap2

  outs aout, aout

  gadist = 0
endin
/* distort1.orc */
        
\end{lstlisting}
\begin{lstlisting}
/* distort1.sco */
;   Sta  Dur  Amp    Pitch
i1  0.0  3.0  10000  6.00
i1  0.5  2.5  10000  7.00
i1  1.0  2.0  10000  7.07
i1  1.5  1.5  10000  8.00
  
;   Sta  Dur  PreGain PostGain Shape1 Shape2
i50 0    3    2       1        0      0
e
/* distort1.sco */
        
\end{lstlisting}
\subsection*{Credits}


 


 


\begin{tabular}{cc}
Author: Hans Mikelson &December 1998

\end{tabular}



 


 New in Csound version 3.50
%\hline 


\begin{comment}
\begin{tabular}{lcr}
Previous &Home &Next \\
display &Up &divz

\end{tabular}


\end{document}
\end{comment}
