\begin{comment}
\documentclass[10pt]{article}
\usepackage{fullpage, graphicx, url}
\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\title{fouti}
\begin{document}


\begin{tabular}{ccc}
The Alternative Csound Reference Manual & & \\
Previous & &Next

\end{tabular}

%\hline 
\end{comment}
\section{fouti}
fouti --  Outputs i-rate signals of an arbitrary number of channels to a specified file. \subsection*{Description}


 \emph{fouti}
 output \emph{N}
 i-rate signals to a specified file of \emph{N}
 channels. 
\subsection*{Syntax}


 \textbf{fouti}
 ihandle, iformat, iflag, iout1 [, iout2, iout3,....,ioutN]
\subsection*{Initialization}


 \emph{ihandle}
 -- a number which specifies this file. 


 \emph{iformat}
 -- a flag to choose output file format: 


 
\begin{itemize}
\item 

 0 - floating point in text format

\item 

 1 - 32-bit floating point in binary format


\end{itemize}


 \emph{iflag}
 -- choose the mode of writing to the ASCII file (valid only in ASCII mode; in binary mode \emph{iflag}
 has no meaning, but it must be present anyway). \emph{iflag}
 can be a value chosen among the following: 


 
\begin{itemize}
\item 

 0 - line of text without instrument prefix

\item 

 1 - line of text with instrument prefix (see below)

\item 

 2 - reset the time of instrument prefixes to zero (to be used only in some particular cases. See below)


\end{itemize}


 \emph{iout,..., ioutN}
 -- values to be written to the file 
\subsection*{Performance}


 \emph{fouti}
 and \emph{foutir}
 write i-rate values to a file. The main use of these opcodes is to generate a score file during a realtime session. For this purpose, the user should set \emph{iformat}
 to 0 (text file output) and \emph{iflag}
 to 1, which enable the output of a prefix consisting of the strings \emph{inum}
, \emph{actiontime}
, and \emph{duration}
, before the values of \emph{iout1...ioutN}
 arguments. The arguments in the prefix refer to instrument number, action time and duration of current note. 


  Notice that \emph{fout}
 and \emph{foutk}
 can use either a string containing a file pathname, or a handle-number generated by \emph{fiopen}
. Whereas, with \emph{fouti}
 and \emph{foutir}
, the target file can be only specified by means of a handle-number. 
\subsection*{See Also}


 \emph{fiopen}
, \emph{fout}
, \emph{foutir}
, \emph{foutk}

\subsection*{Credits}


 


 


\begin{tabular}{ccc}
Author: Gabriel Maldonado &Italy &1999

\end{tabular}



 


 New in Csound version 3.56
%\hline 


\begin{comment}
\begin{tabular}{lcr}
Previous &Home &Next \\
fout &Up &foutir

\end{tabular}


\end{document}
\end{comment}
