\begin{comment}
\documentclass[10pt]{article}
\usepackage{fullpage, graphicx, url}
\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\title{GEN18}
\begin{document}


\begin{tabular}{ccc}
The Alternative Csound Reference Manual & & \\
Previous & &Next

\end{tabular}

%\hline 
\end{comment}
\section{GEN18}
GEN18 --  Writes composite waveforms made up of pre-existing waveforms. \subsection*{Description}


  Writes composite waveforms made up of pre-existing waveforms. Each contributing waveform requires 4 pfields and can overlap with other waveforms. 
\subsection*{Syntax}


 \textbf{f}
 \# time size 18 fna ampa starta finisha fna ampa starta finisha ...
\subsection*{Initialization}


 \emph{size}
 -- number of points in the table. Must be a power-of-2 plus 1 (see f statement). 


 \emph{fna, fnb, etc.}
 -- pre-existing table number to be written into the table. 


 \emph{ampa, ampb, etc.}
 -- strength of wavefoms. These are relative strengths, since the composite waveform may be rescaled later. Negative values are permitted and imply a 180 degree phase shift. 


 \emph{starta, startb, etc.}
 -- where to start writing the fn into the table. 


 \emph{finisha, finishb, etc.}
 -- where to stop writing the fn into the table. 
\subsection*{Examples}


 


 
\begin{lstlisting}
f 1  0  4096  10  1
f 2  0  1025  18  1  1  0  512  1  1  513  1025
        
\end{lstlisting}


 
 f2 consists of two copies of f1 written in to locations 0-512 and 513-1025. \subsection*{Deprecated Names}


 \emph{GEN18}
 was called \emph{GEN22}
 in version 4.18. The name was changed due to a conflict with DirectCsound. 
\subsection*{Credits}


 


 


\begin{tabular}{cccc}
Author: William ``Pete'' Moss &University of Texas at Austin &Austin, Texas USA &January 2002

\end{tabular}



 


 New in version 4.18, changed in version 4.19
%\hline 


\begin{comment}
\begin{tabular}{lcr}
Previous &Home &Next \\
GEN17 &Up &GEN19

\end{tabular}


\end{document}
\end{comment}
