\begin{comment}
\documentclass[10pt]{article}
\usepackage{fullpage, graphicx, url}
\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\title{GEN20}
\begin{document}


\begin{tabular}{ccc}
The Alternative Csound Reference Manual & & \\
Previous & &Next

\end{tabular}

%\hline 
\end{comment}
\section{GEN20}
GEN20 --  Generates functions of different windows. \subsection*{Description}


  This subroutine generates functions of different windows. These windows are usually used for spectrum analysis or for grain envelopes. 
\subsection*{Syntax}


 \textbf{f}
 \# time size 20 window max [opt]
\subsection*{Initialization}


 \emph{size}
 -- number of points in the table. Must be a power of 2 ( + 1). 


 \emph{window}
 -- Type of window to generate: 


 
\begin{itemize}
\item 

 1 = Hamming

\item 

 2 = Hanning

\item 

 3 = Bartlett ( triangle)

\item 

 4 = Blackman ( 3-term)

\item 

 5 = Blackman - Harris ( 4-term)

\item 

 6 = Gaussian

\item 

 7 = Kaiser

\item 

 8 = Rectangle

\item 

 9 = Sync


\end{itemize}


 \emph{max}
 -- For negative p4 this will be the absolute value at window peak point. If p4 is positive or p4 is negative and p6 is missing the table will be post-rescaled to a maximum value of 1. 


 \emph{opt}
 -- Optional argument required by the Kaiser window. 
\subsection*{Examples}


 


 
\begin{lstlisting}
\emph{f}
       1       0       1024    20      5
        
\end{lstlisting}


 
 This creates a function which contains a 4 - term Blackman - Harris window with maximum value of 1. 

 


 
\begin{lstlisting}
\emph{f}
       1       0       1024    -20     2       456
        
\end{lstlisting}


 
 This creates a function that contains a Hanning window with a maximum value of 456. 

 


 
\begin{lstlisting}
\emph{f}
       1       0       1024    -20     1
        
\end{lstlisting}


 
 This creates a function that contains a Hamming window with a maximum value of 1. 

 


 
\begin{lstlisting}
\emph{f}
       1       0       1024    20      7       1       2
        
\end{lstlisting}


 
 This creates a function that contains a Kaiser window with a maximum value of 1. The extra argument specifies how ``open'' the window is, for example a value of 0 results in a rectangular window and a value of 10 in a Hamming like window. 

  For diagrams, see \emph{Window Functions}

\subsection*{Credits}


 


 


\begin{tabular}{ccc}
Author: Paris Smaragdis &MIT, Cambridge &1995

\end{tabular}



 


 


 


\begin{tabular}{ccc}
Author: John ffitch &University of Bath/Codemist Ltd. &Bath, UK

\end{tabular}



 


 New in Csound version 3.2
%\hline 


\begin{comment}
\begin{tabular}{lcr}
Previous &Home &Next \\
GEN19 &Up &GEN21

\end{tabular}


\end{document}
\end{comment}
