\begin{comment}
\documentclass[10pt]{article}
\usepackage{fullpage, graphicx, url}
\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\title{\%}
\begin{document}


\begin{tabular}{ccc}
The Alternative Csound Reference Manual & & \\
Previous & &Next

\end{tabular}

%\hline 
\end{comment}
\section{\%}
\% --  Modulus operator. \subsection*{Description}


  Arithmetic operators perform operations of change-sign (negate), don't-change-sign, logical AND logical OR, add, subtract, multiply and divide. Note that a value or an expression may fall between two of these operators, either of which could take it as its left or right argument, as in 


 a + b * c.\\ 
       


  In such cases three rules apply: 


  1. * and \emph{/}
 bind to their neighbors more strongly than + and \&\#8722;. Thus the above expression is taken as 


   \\ 
 a + (b * c)\\ 
       
 with * taking b and c and then + taking a and b * c. 

  2. \emph{+}
 and \emph{\&\#8722;}
 bind more strongly than \&\&, which in turn is stronger than ||: 


   \\ 
 a \&\& b - c || d\\ 
       
 is taken as 

   \\ 
 (a \&\& (b - c)) || d\\ 
       


  3. When both operators bind equally strongly, the operations are done left to right: 


   \\ 
 a - b - c i\\ 
       
 is taken as 

   \\ 
 (a - b) - c\\ 
       


  Parentheses may be used as above to force particular groupings. 


  The operator \emph{\%}
 returns the value of \emph{a}
 reduced by \emph{b}
, so that the result, in absolute value, is that of the absolute value of \emph{b}
, by repeated subtraction. This is the same as modulus function in integers. New in Csound version 3.50. 
\subsection*{Syntax}


 a \textbf{\%}
 b (no rate restriction)


  where the arguments \emph{a}
 and \emph{b}
 may be further expressions. 
\subsection*{Examples}


  Here is an example of the \% operator. It uses the files \emph{modulus.orc}
 and \emph{modulus.sco}
. 


 \textbf{Example 1. Example of the \% operator.}

\begin{lstlisting}
/* modulus.orc */
; Initialize the global variables.
sr = 44100
kr = 4410
ksmps = 10
nchnls = 1

; Instrument #1.
instr 1
  i1 = 5 % 3
  print i1
endin
/* modulus.orc */
        
\end{lstlisting}
\begin{lstlisting}
/* modulus.sco */
; Play Instrument #1 for one second.
i 1 0 1
e
/* modulus.sco */
        
\end{lstlisting}
 Its output should include a line like this: \begin{lstlisting}
instr 1:  i1 = 2.000
      
\end{lstlisting}
\subsection*{See Also}


 \emph{-}
, \emph{+}
, \emph{\&\&}
, \emph{||}
, \emph{*}
, \emph{/}
, \emph{\^{}}

\subsection*{Credits}


 Example written by Kevin Conder.
%\hline 


\begin{comment}
\begin{tabular}{lcr}
Previous &Home &Next \\
\$NAME &Up &\&\&

\end{tabular}


\end{document}
\end{comment}
