\begin{comment}
\documentclass[10pt]{article}
\usepackage{fullpage, graphicx, url}
\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\title{Copyright Notice}
\begin{document}


\begin{tabular}{ccc}
The Alternative Csound Reference Manual & & \\
Previous &Preface &Next

\end{tabular}

%\hline 
\end{comment}
\section{Copyright Notice}


  Copyright (c) 1986, 1992 by the Massachusetts Institute of Technology. All rights reserved. 


  Developed by \emph{Barry L. Vercoe}
 at the Experimental Music Studio, Media Laboratory, M.I.T., Cambridge, Massachusetts, with partial support from the System Development Foundation and from National Science Foundation Grant \# IRI-8704665. 


  Copyright (c) 2003 by Kevin Conder for modifications made to the Public Csound Reference Manual. 


  Permission is granted to copy, distribute and/or modify this document under the terms of the GNU Free Documentation License, Version 1.2 or any later version published by the Free Software Foundation; with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts. A copy of this license is available in the examples sub-directory. 


  A legal notice from the Public Csound Reference Manual... ``The original Hypertext Edition of the MIT Csound Manual was prepared for the World Wide Web by \emph{Peter J. Nix}
 of the Department of Music at the University of Leeds and \emph{Jean Pich\'e}
 of the Facult\'e de musique de l'Universit\'e de Montr\'eal. A Print Edition, in Adobe Acrobat format, was then maintained by \emph{David M. Boothe}
. The editors fully acknowledge the rights of the authors of the original documentation and programs, as set out above, and further request that this notice appear wherever this material is held.''


  The Public Csound Reference Manual's last known network location was \url{http://www.lakewoodsound.com/csound/hypertext/manual.htm}. 


  The Alternative Csound Reference Manual's network location, for both the Transparent and Opaque copies, is \url{http://kevindumpscore.com/download.html}\#csound-manual. 
%\hline 


\begin{comment}
\begin{tabular}{lcr}
Previous &Home &Next \\
Preface &Up &Acknowledgements

\end{tabular}


\end{document}
\end{comment}
