\begin{comment}
\documentclass[10pt]{article}
\usepackage{fullpage, graphicx, url}
\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\title{pvsadsyn}
\begin{document}


\begin{tabular}{ccc}
The Alternative Csound Reference Manual & & \\
Previous & &Next

\end{tabular}

%\hline 
\end{comment}
\section{pvsadsyn}
pvsadsyn --  Resynthesize using a fast oscillator-bank. \subsection*{Description}


  Resynthesize using a fast oscillator-bank. 
\subsection*{Syntax}


 ar \textbf{pvsadsyn}
 fsrc, inoscs, kfmod [, ibinoffset] [, ibinincr] [, iinit]
\subsection*{Initialization}


 \emph{inoscs}
 -- The number of analysis bins to synthesise. Cannot be larger than the size of fsrc (see \emph{pvsinfo}
), e.g. as created by \emph{pvsanal}
. Processing time is directly proportional to inoscs. 


 \emph{ibinoffset}
 (optional, default=0) -- The first (lowest) bin to resynthesise, counting from 0 (default = 0). 


 \emph{ibinincr}
 (optional) -- Starting from bin ibinoffset, resynthesize bins ibinincr apart. 


 \emph{iinit}
 (optional) -- Skip reinitialization. This is not currently implemented for any of these opcodes, and it remains to be seen if it is even practical. 
\subsection*{Performance}


 \emph{kfmod}
 -- Scale all frequencies by factor kfmod. 1.0 = no change, 2 = up one octave. 


 \emph{pvsadsyn}
 is experimental, and implements the oscillator bank using a fast direct calculation method, rather than a lookup table. This takes advantage of the fact, empirically arrived at, that for the analysis rates generally used, (and presuming analysis using \emph{pvsanal}
, where frequencies in a bin change only slightly between frames) it is not necessary to interpolate frequencies between frames, only amplitudes. Accurate resynthesis is often contingent on the use of pvsanal with iwinsize = ifftsize*2. 


  This opcode is the most likely to change, or be much extended, according to feedback and advice from users. It is likely that a full interpolating table-based method will be added, via a further optional iarg. The parameter list to pvsadsyn mimics that for \emph{pvadd}
, but excludes spectral extraction. 
\subsection*{Examples}


 


 
\begin{lstlisting}
; resynth the first 100 odd-numbered bins, with pitch scaling envelope.
kpch  linseg    1,p3/3,1,p3/3,1.5,p3/3,1
aout  pvsadsyn  fsrc, 100,kpch,1,2
        
\end{lstlisting}


 
\subsection*{See Also}


 \emph{pvsynth}

\subsection*{Credits}


 


 


\begin{tabular}{cc}
Author: Richard Dobson &August 2001 

\end{tabular}



 


 New in version 4.13
%\hline 


\begin{comment}
\begin{tabular}{lcr}
Previous &Home &Next \\
pvread &Up &pvsanal

\end{tabular}


\end{document}
\end{comment}
