\begin{comment}
\documentclass[10pt]{article}
\usepackage{fullpage, graphicx, url}
\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\title{spat3dt}
\begin{document}


\begin{tabular}{ccc}
The Alternative Csound Reference Manual & & \\
Previous & &Next

\end{tabular}

%\hline 
\end{comment}
\section{spat3dt}
spat3dt --  Can be used to render an impulse response for a 3D space at i-time. \subsection*{Description}


  This opcode positions the input sound in a 3D space, with optional simulation of room acoustics, in various output formats. \emph{spat3dt}
 can be used to render the impulse response at i-time, storing output in a function table, suitable for convolution. 
\subsection*{Syntax}


 \textbf{spat3dt}
 ioutft, iX, iY, iZ, idist, ift, imode, irlen [, iftnocl]
\subsection*{Initialization}


 \emph{ioutft}
 -- Output ftable number for spat3dt. W, X, Y, and Z outputs are written interleaved to this table. If the table is too short, output will be truncated. 


 \emph{iX}
 -- Sound source X coordinate in meters (positive: right, negative: left) 


 \emph{iY}
 -- Sound source Y coordinate in meters (positive: front, negative: back) 


 \emph{iZ}
 -- Sound source Z coordinate in meters (positive: up, negative: down) 


 \emph{idist}
 -- For modes 0 to 3, \emph{idist}
 is the unit circle distance in meters. For mode 4, \emph{idist}
 is the distance between microphones. 


  The following formulas describe amplitude and delay as a function of sound source distance from microphone(s): 


 amplitude = 1 / (0.1 + distance)\\ 
       


 delay = distance / 340 (in seconds)\\ 
       


  Distance can be calculated as: 


 distance = sqrt(iX\^{}2 + iY\^{}2 + iZ\^{}2)\\ 
       
 In Mode 4, distance can be calculated as: 

 distance from left mic = sqrt((iX + idist/2)\^{}2 + iY\^{}2 + iZ\^{}2)\\ 
 distance from right mic = sqrt((iX - idist/2)\^{}2 + iY\^{}2 + iZ\^{}2)\\ 
       


  With \emph{spat3d}
 the distance between the sound source and any microphone should be at least (340 * 18) / sr meters. Shorter distances will work, but may produce artifacts in some cases. There is no such limitation for \emph{spat3di}
 and \emph{spat3dt}
. 


  Sudden changes or discontinuities in sound source location can result in pops or clicks. Very fast movement may also degrade quality. 


 \emph{ift}
 -- Function table storing room parameters (for free field spatialization, set it to zero or negative). Table size is 64. The values in the table are: 


 


\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
%\hline 
Room ParameterPurpose & & & & & & & & & & & & & & \\
 %\hline 
0Early reflection recursion depth (0 is the sound source, 1 is the first reflection etc.) for spat3d and spat3di. The number of echoes for four walls (front, back, right, left) is: N = (2*R + 2) * R. If all six walls are enabled: N = (((4*R + 6)*R + 8)*R) / 3 &1Late reflection recursion depth (used by spat3dt only). spat3dt skips early reflections and renders echoes up to this level. If early reflection depth is negative, spat3d and spat3di will output zero, while spat3dt will start rendering from the sound source. &2imdel for spat3d. Overrides opcode parameter if non-negative. &3irlen for spat3dt. Overrides opcode parameter if non-negative. &4idist value. Overrides opcode parameter if $>$= 0. &5Random seed (0 - 65535) -1 seeds from current time. &6 - 53wall parameters (w = 6: ceil, w = 14: floor, w = 22: front, w = 30: back, w = 38: right, w = 46: left) &w + 0Enable reflections from this wall (0: no, 1: yes) &w + 1Wall distance from listener (in meters) &w + 2Randomization of wall distance (0 - 1) (in units of 1 / (wall distance)) &w + 3Reflection level (-1 - 1) &w + 4Parametric equalizer frequency in Hz. &w + 5Parametric equalizer level (1.0: no filtering) &w + 6Parametric equalizer Q (0.7071: no resonance) &w + 7Parametric equalizer mode (0: peak EQ, 1: low shelf, 2: high shelf) \\
 %\hline 

\end{tabular}



 


 \emph{imode}
 -- Output mode 


 
\begin{itemize}
\item 

 0: B format with W output only (mono) 


 aout    =  aW

\item 

 1: B format with W and Y output (stereo) 


 aleft   =  aW + 0.7071*aY\\ 
 aright  =  aW - 0.7071*aY

\item 

 2: B format with W, X, and Y output (2D). This can be converted to UHJ: 


 aWre, aWim      hilbert aW\\ 
 aXre, aXim      hilbert aX\\ 
 aYre, aYim      hilbert aY\\ 
 aWXr    =  0.0928*aXre + 0.4699*aWre\\ 
 aWXiYr  =  0.2550*aXim - 0.1710*aWim + 0.3277*aYre\\ 
 aleft   =  aWXr + aWXiYr\\ 
 aright  =  aWXr - aWXiYr

\item 

 3: B format with all outputs (3D)

\item 

 4: Simulates a pair of microphones (stereo output) 


 aW      butterlp aW, ifreq      ; recommended values for ifreq\\ 
 aY      butterlp aY, ifreq      ; are around 1000 Hz\\ 
 aleft   =  aW + aX\\ 
 aright  =  aY + aZ


\end{itemize}


  Mode 0 is the cheapest to calculate, while mode 4 is the most expensive. 


  In Mode 4, The optional lowpass filters can change the frequency response depending on direction. For example, if the sound source is located left to the listener then the high frequencies are attenuated in the right channel and slightly increased in the left. This effect can be disabled by not using filters. You can also experiment with other filters (tone etc.) for better effect. 


  Note that mode 4 is most useful for listening with headphones, and is also more expensive to calculate than the B-format (0 to 3) modes. The \emph{idist}
 parameter in this case sets the distance between left and right microphone; for headphones, values between 0.2 - 0.25 are recommended, although higher settings up to 0.4 may be used for wide stereo effects. 


  More information about B format can be found here: \emph{\url{http://www.york.ac.uk/inst/mustech/3d}\_audio/ambis2.htm}



 \emph{irlen}
 -- Impulse response length of echoes (in seconds). Depending on filter parameters, values around 0.005-0.01 are suitable for most uses (higher values result in more accurate output, but slower rendering) 


 \emph{iftnocl}
 (optional, default=0) -- Do not clear output ftable (mix to existing data) if set to 1, clear table before writing if set to 0 (default: 0). 
\subsection*{Performance}


  If you encounter very slow performance (up to 100 times slower), it may be caused by denormals (this is also true of many other IIR opcodes, including \emph{butterlp}
, \emph{pareq}
, \emph{hilbert}
, and many others). Underflows can be avoided by: 


 
\begin{itemize}
\item 

 mixing low level DC or noise to the input signal, e.g. 


 atmp rnd31 1/1e24, 0, 0


 aW, aX, aY, aZ spa3di ain + atmp, ...
 or 

 aW, aX, aY, aZ spa3di ain + 1/1e24, ...

\item 

 reducing \emph{irlen}
 in the case of \emph{spat3dt}
 (which does not have an input signal). A value of about 0.005 is suitable for most uses, although it also depends on EQ settings. If the equalizer is not used, ``irlen'' can be set to 0.


\end{itemize}
\subsection*{Examples}


  See the examples for \emph{spat3d}
. 
\subsection*{See Also}


 \emph{spat3d}
, \emph{spat3di}

\subsection*{Credits}


 


 


\begin{tabular}{cc}
Author: Istvan Varga &2001

\end{tabular}



 


 New in version 4.12


 Updated April 2002 by Istvan Varga
%\hline 


\begin{comment}
\begin{tabular}{lcr}
Previous &Home &Next \\
spat3di &Up &spdist

\end{tabular}


\end{document}
\end{comment}
