\begin{comment}
\documentclass[10pt]{article}
\usepackage{fullpage, graphicx, url}
\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\title{zfilter2}
\begin{document}


\begin{tabular}{ccc}
The Alternative Csound Reference Manual & & \\
Previous & &Next

\end{tabular}

%\hline 
\end{comment}
\section{zfilter2}
zfilter2 --  Performs filtering using a transposed form-II digital filter lattice with radial pole-shearing and angular pole-warping. \subsection*{Description}


  General purpose custom filter with time-varying pole control. The filter coefficients implement the following difference equation: 


 (1)*y(n) = b0*x[n] + b1*x[n-1] +...+ bM*x[n-M] - a1*y[n-1] -...- aN*y[n-N]\\ 
       


  the system function for which is represented by: 


            B(Z)      b0 + b1*Z-1  + ... + bM*Z-M\\ 
   H(Z)  =  ----  =  --------------------------\\ 
            A(Z)       1 + a1*Z-1  + ... + aN*Z-N\\ 
       
\subsection*{Syntax}


 ar \textbf{zfilter2}
 asig, kdamp, kfreq, iM, iN, ib0, ib1, ..., ibM, ia1,ia2, ..., iaN
\subsection*{Initialization}


  At initialization the number of zeros and poles of the filter are specified along with the corresponding zero and pole coefficients. The coefficients must be obtained by an external filter-design application such as Matlab and specified directly or loaded into a table via \emph{GEN01}
. With \emph{zfilter2}
, the roots of the characteristic polynomials are solved at initialization so that the pole-control operations can be implemented efficiently. 
\subsection*{Performance}


  The \emph{filter2}
 opcodes perform filtering using a transposed form-II digital filter lattice with no time-varying control. \emph{zfilter2}
 uses the additional operations of radial pole-shearing and angular pole-warping in the Z plane. 


  Pole shearing increases the magnitude of poles along radial lines in the Z-plane. This has the affect of altering filter ring times. The k-rate variable \emph{kdamp}
 is the damping parameter. Positive values (0.01 to 0.99) increase the ring-time of the filter (hi-Q), negative values (-0.01 to -0.99) decrease the ring-time of the filter, (lo-Q). 


  Pole warping changes the frequency of poles by moving them along angular paths in the Z plane. This operation leaves the shape of the magnitude response unchanged but alters the frequencies by a constant factor (preserving 0 and p). The k-rate variable \emph{kfreq}
 determines the frequency warp factor. Positive values (0.01 to 0.99) increase frequencies toward p and negative values (-0.01 to -0.99) decrease frequencies toward 0. 


  Since \emph{filter2}
 implements generalized recursive filters, it can be used to specify a large range of general DSP algorithms. For example, a digital waveguide can be implemented for musical instrument modeling using a pair of \emph{delayr}
 and \emph{delayw}
 opcodes in conjunction with the \emph{filter2}
 opcode. 
\subsection*{Examples}


  A controllable second-order IIR filter operating on an a-rate signal: 


 
\begin{lstlisting}
a1 \emph{zfilter2}
 asig, kdamp, kfreq, 1, 2, 1, ia1, ia2 ; controllable a-rate   ; IIR filter
        
\end{lstlisting}


 
\subsection*{See Also}


 \emph{filter2}

\subsection*{Credits}


 


 


\begin{tabular}{cccc}
Author: Michael A. Casey &M.I.T. &Cambridge, Mass. &1997

\end{tabular}



 
%\hline 


\begin{comment}
\begin{tabular}{lcr}
Previous &Home &Next \\
zawm &Up &zir

\end{tabular}


\end{document}
\end{comment}
